---
title: "Final Project"
author: "Jaiveer Katariya"
date: "11/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
## Introduction


## Background



## Procedure
 Explain ordering of questions
 Explain tweet selection process
 Explain coming up with engagement options, why they matter
 Explain emotional scale

## Results

### Exploratory Data Analysis
To begin, we'll load the data in from the aforementioned formatted csv and perform some exploratory data analysis. 

```{r}
data <- read.csv('formatted_responses.csv')
numberRespondents <- unique(data$Respondent) %>%
  length
num_uni <- unique(data$College) %>%
  length()

numberRespondents
num_uni
  
```

Through the data collection methods above, responses were collected from 204 students attending 48 different universities. These were both public and private universities scattered throughout the country from the University of Florida to Stanford University. 

This variety of colleges likely had an impact on the next statistic observed - the respondents' political stances. 

```{r}
ideology <- data %>%
  group_by(Ideology) %>%
  summarise(count=n()*100/3654) 

ideology

ideology %>%
  ggplot(aes(x="", y=count, fill=Ideology)) + 
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) + theme_void()

```


As expected, the vast majority of college students identified themselves as being left of center. Given the well known phenomenon that college students will generally be left of center, going into the experiment, one concern was that there wasn't going to be enough representation of right-wing political viewpoints. Though the validity of the data has yet to be seen in additional tests, nearly a quarter of respondents identified as either centrists or right of center, which was a greater portion than initially expected. 

As for the tweets themselves, it may be of use to get a sense of what people's responses were to them on average. 

```{r}
data %>%
  group_by(Tweet) %>%
  summarise(
    average_like = mean(Engagement_Like)
  ) %>%
  ggplot(aes(x=average_like)) + geom_histogram(bindwidth=0.01) + theme_minimal()

data %>%
  group_by(Tweet) %>%
  summarise(
    average_retweet_without = mean(Engagement_Retweet.without.quote)
  ) %>%
  ggplot(aes(x=average_retweet_without)) + geom_histogram(bindwidth=0.01) + theme_minimal()

data %>%
  group_by(Tweet) %>%
  summarise(
    average_retweet_with = mean(Engagement_Retweet.with.quote)
  ) %>%
  ggplot(aes(x=average_retweet_with)) + geom_histogram(bindwidth=0.01) + theme_minimal()

data %>%
  group_by(Tweet) %>%
  summarise(
     average_view_replies = mean(Engagement_View.replies)
  ) %>%
  ggplot(aes(x=average_view_replies)) + geom_histogram(bindwidth=0.01) + theme_minimal()

data %>%
  group_by(Tweet) %>%
  summarise(
    average_profile_click = mean(Engagement_Click.on.author.s.profile)
  ) %>%
  ggplot(aes(x=average_profile_click)) + geom_histogram(bindwidth=0.01) + theme_minimal()

data %>%
  group_by(Tweet) %>%
  summarise(
    average_write_reply = mean(Engagement_Write.reply)
  ) %>%
  ggplot(aes(x=average_write_reply)) + geom_histogram(bindwidth=0.01) + theme_minimal()

data %>%
  group_by(Tweet) %>%
  summarise(
    average_ignore = mean(Engagement_Ignore.keep.scrolling)
  ) %>%
  ggplot(aes(x=average_ignore)) + geom_histogram(bindwidth=0.01) + theme_minimal()


```

In the above graphs, each engagement type (which was assigned a 1 if users selected that method of engagement and 0 if not) was averaged for each tweet, giving the portion of users that performed that engagement for each tweet. The above histograms are therefore meant to describe how often users were performing each type of engagement across the entire corpus of tweets.

First, understandably, a significant number of tweets received either little to no likes or a "likes" average of around 0.5. Therefore, it seems as though many tweets were either widely liked (closer to being liked by about half the respondents), or widely not liked (receiving likes from almost 0% of respondents). Given the political nature of these tweets, these disparate scores may be a result of the heavy left-leaning bias that exists in the respondents. If most of the respondents were left leaning, then it makes sense that most of the respondents would act similarly, either uniformly liking or not liking a tweet. While it may be pointed out that a "like" rate of 0.5 does not indicate a "uniform liking" of the tweet by the respondents, the distinct separation between the two peaks in the histogram is certainly worth noting.

The next engagement pattern, retweets without quotes, shows a slightly different story. While a few tweets were, on average, retweeted occasionally (between 10 and 20% of the time), the vast majority of tweets were retweeted rarely, if ever. While not as indicative of any sort of political bias among the respondents, this pattern is somewhat of a different expected trend: people's reluctance to publicly engage with political content in general, and therefore the controversial subject matter intentionally selected for this study. Retweets, more than any kind of engagement, clearly associate the user with the content being retweeted to the public eye. This is a consequence that many college students, whether or not they're seeking professional and academic opportunities, may not want to inflict upon themselves, and as a result, they may be hesitant to retweet this controversial, polarizing content. We can observe a similar pattern for retweets with quotes, which respondents were even less likely to perform; likely for the same aforementioned reasons.

Yet another distinct pattern can be observed for viewing replies, which makes sense. Unlike the first three forms of engagement, viewing replies is not a form of engagement that is directly visible to one's following. As a result, it may be a form of engagement that users are more likely to do across all tweets. This was, to some extent, reflected in the above histogram. Just about every tweet had its replies viewed between 20 and 40 percent of the time, with a single outlier on each side of that interval. 

Next, though viewing author profiles are also a private form of engagement, users seemed to be far less likely to do that than to view replies, with most tweets having their replies viewed between 5 and 10 percent of the time.

By far the least common form of engagement taken was writing replies to the tweet, likely for the same reasons that caused the low frequencies of retweets. The two tweets in which this response was the most common had less than five percent of respondents indicate that they would do so.

In a move completely contradictory to many of the assumptions introduced in the background of this study, ignoring tweets seemed to be, by far, the most common response to the tweets in this study, with the least-ignored tweets being ignored 30-40% of the time, and the most frequently ignored tweets being ignored over 70% of the time. This outcome may be due to a number of factors, including the time at which this survey was conducted: the weeks leading up to the 2020 Presidential Election. Most respondents had probably been overexposed to political content leading up to the survey, and as a result, were probably desensitized to much of the content on the survey. This may have resulted in a higher rate of apathy towards the political content than if the survey were conducted at a different, less politicized time of year. One may compare this phenomenon to the playing of Christmas carols in public spaces throughout the United States during the holiday season. The first listening of Mariah Carey's "All I Want for Christmas is You" may fill many with a warm, pleasant feeling inside, but by late December, most are numb to the amorous holiday-themed lyrics and upbeat melody.



Before investigating correlations involving emotional reactions to the tweets, an analysis similar to the one conducted for engagement may be of some worth. The histograms below show the portion of users that had each emotional response for each tweet.

```{r}
data %>%
  group_by(Tweet) %>%
  summarise(
    average_joy = mean(Reaction_Joy)
  ) %>%
  ggplot(aes(x=average_joy)) + geom_histogram(bindwidth=0.01) + theme_minimal()

data %>%
  group_by(Tweet) %>%
  summarise(
    average_sadness = mean(Reaction_Sadness)
  ) %>%
  ggplot(aes(x=average_sadness)) + geom_histogram(bindwidth=0.01) + theme_minimal()

data %>%
  group_by(Tweet) %>%
  summarise(
    average_relief = mean(Reaction_Relief)
  ) %>%
  ggplot(aes(x=average_relief)) + geom_histogram(bindwidth=0.01) + theme_minimal()

data %>%
  group_by(Tweet) %>%
  summarise(
     average_distress = mean(Reaction_Distress)
  ) %>%
  ggplot(aes(x=average_distress)) + geom_histogram(bindwidth=0.01) + theme_minimal()

data %>%
  group_by(Tweet) %>%
  summarise(
    average_hope = mean(Reaction_Hope)
  ) %>%
  ggplot(aes(x=average_hope)) + geom_histogram(bindwidth=0.01) + theme_minimal()

data %>%
  group_by(Tweet) %>%
  summarise(
    average_fear = mean(Reaction_Fear)
  ) %>%
  ggplot(aes(x=average_fear)) + geom_histogram(bindwidth=0.01) + theme_minimal()


data %>%
  group_by(Tweet) %>%
  summarise(
    average_empathy = mean(Reaction_Empathy)
  ) %>%
  ggplot(aes(x=average_empathy)) + geom_histogram(bindwidth=0.01) + theme_minimal()

data %>%
  group_by(Tweet) %>%
  summarise(
    average_frustration = mean(Reaction_Frustration)
  ) %>%
  ggplot(aes(x=average_frustration)) + geom_histogram(bindwidth=0.01) + theme_minimal()

data %>%
  group_by(Tweet) %>%
  summarise(
    average_frustration = mean(Reaction_Frustration)
  ) %>% 
  arrange(desc(average_frustration))

data %>%
  group_by(Tweet) %>%
  summarise(
    average_agreement = mean(Reaction_Agreement)
  ) %>%
  ggplot(aes(x=average_agreement)) + geom_histogram(bindwidth=0.01) + theme_minimal()

data %>%
  group_by(Tweet) %>%
  summarise(
    average_dissension = mean(Reaction_Dissension)
  ) %>%
  ggplot(aes(x=average_dissension)) + geom_histogram(bindwidth=0.01) + theme_minimal()

data %>%
  group_by(Tweet) %>%
  summarise(
    average_apathy = mean(Reaction_NONE)
  ) %>%
  ggplot(aes(x=average_apathy)) + geom_histogram(bindwidth=0.01) + theme_minimal()
```

To begin, little to no joy was felt by respondents for just about every tweet in the corpus, with most being near an average of 0% of respondents reporting joy. The single outlier in the data seems to be a tweet for which only 8% of respondents felt joy. This graph can be said to demonstrate, to at least some capacity, how little joy political Twitter brings to college students. While these data can be interpreted to convey that college students simply don't enjoy politics, perhaps the more likely reason for this outcome is the current emotional climate of political content on Twitter.

The negative counterpart to joy in this study was sadness, which seemed to be a much more popular response across the entire corpus. Though still reported in less than half of respondents for every tweet, the portions of responses that report sadness are generally significantly higher. 

The same trend seems to be even more exaggerated in the next pair of emotions, relief and distress. In a response that aligned perfectly with the earlier description of today's political climate, distress seemed to be a much more common response to the displayed tweets than relief. While most tweets incited distress in 10 to 30 percent of respondents, most tweets fostered relief in less than 1% of the respondents who saw them. These trends are indicative of the very issue that motivated this paper: political content on Twitter is outrage-inducing. Whether or not this phenomenon is intentional, it is an issue that absolutely needs to be better understood for the sake of the entire US population.

While the scales are not dramatically different in the graphs showing the portions of respondents who reacted to each tweet with fear and hope, the graph for the former seems to be more normally distributed than the right-skewed graph for the latter. While fear was not exactly common, with most tweets triggering fear in less than 15% of the respondents, there were several that did so in more than 20% of the respondents. Meanwhile, only two tweets inspired hope in 10% or more of the respondents, indicating that, at least for the tweets that were intentionally selected to be controversial, fear tended to be a much more common reaction than hope. 

A great demonstrator of the polarizing nature of political tweets is the disparity in responses among the next pair of emotional responses, frustration and empathy. Continuing the trend, there were many more tweets that elicited the negative emotion in a high portion of respondents than tweets that elicited the positive emotion. While most tweets inspired empathy in less than 10% of the respondents, almost every tweet provoked frustration in more than 30% of the respondents, with several provoking frustration in more than 60% of the respondents. These widely-frustrating tweets were tweets 14, 6, and 10, which, in order, called the coronavirus a hoax, showed protesters clashing with law enforcement officers to the glee of the tweet author, and defended a white supremacist group. If political tweets are, on average, generating more frustration than empathy in their audiences, then it only makes sense that those audiences will become increasingly polarized and divided.

The last pair of emotions provided to respondents were dissension and agreement. The two had similar distributions: tweets either incited these emotions in more than 30% of the respondents, or in less than 10%. One feature worth nothing though is that there were several tweets that garnered agreement from more than 50% of the users, while there was only one such tweet for dissension. This may be indicative of a political bias in the respondents or in the survey On one hand, the respondents may have disproportionately agreed upon certain political messages. On the other, the survey may have contained a disproportionately large number of tweets that were widely agreeable across all political groups. Determining which kind of bias exists, and the extent to which it exists, would likely require more testing with a larger set of tweets and a larger sample population.

In addition to the aforementioned emotional responses, respondents also had the option to mark "NONE", indicating that they had no significant emotional response. Half of the tweets had between 20 and 40% of the respondents mark this as their response, while the rest of the tweets were just outside this range. This was especially interesting given one of the assumptions reached in the background of this paper, which stated that it would make sense for political content generators to produce intentionally emotionally-charged content since emotionally-charged content will generally spread more and draw more participation than purely reason-based content. However, it is possible that the content was emotionally charged, and, as was said before, respondents had simply been overexposed to political content prior to taking the survey. As a result, respondents may have been much more likely to feel apathetic to the content in the survey than if they hadn't taken the survey in the weeks leading up to a presidential election, therefore causing the high rates of apathy for the tweets in the survey.

### Relationships Between Political Stance, Emotional Reaction, and Engagement
Before diving directly into the relationship between individuals' emotional response to political content and their engagement with it, it may be valuable to first understand how their political beliefs affect their engagement. After all, it only makes sense that one's emotional disposition regarding political tweets would be heavily influenced by their political beliefs. Therefore, any relationship between people's ideological stances and their engagement may provide context necessary to this study's attempt at answering the focal question.

The following graphs show, for each tweet, how engagement varied across two political groups: respondents who identified as moderately liberal, liberal, or extremely liberal, and respondents who identified as centrist, moderately conservative, conservative, or extremely conservative. Centrists were grouped in with the second category since, even without it, the first group already holds the vast majority of the respondents.

```{r}

# dividing respondents into two groups
data <- data %>%
  mutate(political_group = case_when(
    Ideology == "Moderately Liberal" | Ideology == "Liberal" | Ideology == "Extremely liberal" ~ "Left",
    TRUE ~ "Not Left"
  ))

gen_engagement_graph <- function(tweetNumber){
  toReturn <- data %>%
    filter(Tweet==tweetNumber) %>%
    dplyr::select(Engagement_Like, Engagement_Retweet.with.quote, Engagement_Retweet.without.quote, Engagement_Click.on.author.s.profile, Engagement_View.replies, Engagement_Write.reply, Engagement_Ignore.keep.scrolling, political_group) %>%
    group_by(political_group) %>%
    summarise(
      like_proportion = mean(Engagement_Like),
      rt_without_proportion = mean(Engagement_Retweet.without.quote),
      rt_with_proportion = mean(Engagement_Retweet.with.quote),
      click_profile_proportion = mean(Engagement_Click.on.author.s.profile),
      view_replies_proportion = mean(Engagement_View.replies),
      write_replies_proportion = mean(Engagement_Write.reply),
      ignore_proportion = mean(Engagement_Ignore.keep.scrolling)
    ) %>%
    gather(key = Engagement, value = Proportion, like_proportion:ignore_proportion) %>%
    ggplot(aes(Engagement, Proportion, fill = political_group)) + geom_col(position = "dodge")+ coord_flip() + labs(title = paste(c("Tweet", tweetNumber), collapse = " ")) 

  return(toReturn)
}

```

```{r}
gen_engagement_graph(1)

```

Tweet 1, which was made by a democrat running for Congress, expressed desire for policies currently being fought for by the left, including an expansion of public education and governmental healthcare and, most notably, a "Green New Deal". Engagement of all kinds were significantly more common among respondents in the "left" group apart from writing replies. Slightly more than 20% of respondents in both political groups viewed the Tweet's replies, with respondents not identifying with the left viewing replies slightly more frequently. Writing replies was also infrequent for both groups, but was significantly more frequent for non-left respondents.


```{r}
gen_engagement_graph(2)

```

Tweet 2 discussed the controversial, widespread destruction of property that took place after the murder of George Floyd in late May and early June. Likes and both kinds of retweets were more common among left-identifying responses, but non-left respondents viewed replies with almost the same frequency and wrote replies with greater frequency. Nearly twice as many non-left respondents ignored the tweet as left-identifying respondents.


```{r}
gen_engagement_graph(3)

```

Tweet 3 criticized Democratic presidential candidate Joe Biden's refusal to condemn the "Marxist" leaders of the leftist "Black Lives Matter" movement. Given the aggressive nature of the tweet, very few respondents opted to retweet it, and though the only respondents that liked it were non-left, less than 10% of respondents in that group liked it anyway. Many respondents completely ignored the tweet, with more than 50% of left-identifying respondents opting to do so. Interestingly enough, frequencies of private engagement remained relatively high for both groups, with more than 40% of left-identifying respondents viewing the replies, and just over 20% of both groups clicking on the author's profile.


```{r}
gen_engagement_graph(4)

```

Tweet 4 discussed a video in which individuals spray painted messages on the road in front a home with pro-Trump signage in a predominantly liberal neighborhood. All forms of engagement were relatively low, with roughly 60 percent of both groups simply ignoring the tweet, but once again, viewing the replies of the tweet was quite common, with nearly 40% of respondents in both groups indicating that they would do so. This seems to be evidence of a growing trend of individuals stepping across ideological lines to view the replies of Tweets filled with content that they may disagree with, thereby engaging with them. 

```{r}
gen_engagement_graph(5)

```

Tweet 5 is a skeptical claim that Trump was trying to push a Supreme Court nominee so that in the event that the outcome of the election went to them, the court would be more likely to rule in favor of Trump. Non-left respondents ignored this tweet at an extremely high rate, with almost 80% of them indicating that they would do so. However, nearly 20% of the respondents in this group opted to view the tweet's replies, with just over 30% of left-identifying respondents indicating they would also do the same. 

```{r}
gen_engagement_graph(6)

```

Tweet 6 describes a video in which, as the author describes, the "Secret Service pushes back liberal thugs at the white house". The tweet author also calls the COVID-19 pandemic a hoax. While just about 60% of the respondents in both groups opted to ignore the tweet, nearly 40% of both groups indicated that they would view the tweet's replies. This is especially interesting, since despite the controversial nature of the tweet, significant portions of both groups choose to engage with the tweet.

```{r}
gen_engagement_graph(7)

```

Tweet 7 makes a comparison between left-wing and right-wing "extremism", putting the former in a much more positive light. This clear bias may explain why so many of the left-identifying respondents liked the tweet, over 40%. However, once again, both groups viewed replies quite frequently, with non-left respondents at just over 20%, and left-identifying respondents at nearly 30%. Nearly 10% of both groups also chose to click on the author's profile.

```{r}
gen_engagement_graph(8)

```

Tweet 8 was an exclamation by FLorida Representative Matt Gaetz that Republicans wanted to "OPEN AMERICA UP" rather than lock it down as a response to the pandemic. More than 60% of both groups ignored the tweet, but for those who didn't, non-left respondents liked and retweeted the tweet at a higher rate, but left-identifying respondents indicated they would click on the author's profile, view replies, or write a reply more often than non-left respondents. 

```{r}
gen_engagement_graph(9)

```

Tweet 9, written by Bernie Sanders, points out the fact that Donald Trump has paid substantially more in tax dollars to other countries than he has in the United States. Unsurprisingly, left-identifying respondents engaged with the content more frequently in almost every category. Another notable feature of the graph is that once again, over 20% of both left-identifying and non-left respondents wanted to view the tweet's replies.

```{r}
gen_engagement_graph(10)

```

Tweet 10 contained a message defending the "Proud Boys", a white supremacist group, citing the fact that the author hadn't heard of this group doing any kind of "looting, torching, or rioting." Once again, most respondents either ignored the controversial tweet or viewed its replies, but interestingly, this tweet had a higher rate than others of respondents from both groups indicating that they would write a reply. Over 10% of non-left respondents indicated that they would like the tweet, indicating perhaps another potential source that controversial tweets could easily spread: simply by users who agree with the message propagating it to their followers. 

```{r}
gen_engagement_graph(11)

```

Tweet 11 discusses the recent confirmation of Amy Cohen Barrett to the Supreme Court, saying that the left has no "moral authority to stand on... after what they did to Brett Kavanaugh". Oddly enough, left-identifying respondents indicated they would retweet with a quote more frequently than non-left respondents, but both likes and retweets without a quote were significantly more frequent among non-left respondents than left-identifying respondents. Once again, a significant portion of respondents from both groups indicated that they would view the tweet's replies, with a higher portion of left-identifying respondents indicating that they would do so (nearly 30%!) despite the fact that the tweet promotes a right-wing viewpoint.

```{r}
gen_engagement_graph(12)

```

In tweet 12, Bernie Sanders points out that Amazon has paid nearly nothing in federal income taxes over the last three years. A significant number of both left-identifying and non-left respondents "liked" the tweet, with 60% of the first category and over 20% of the second category of respondents doing so. Retweet and profile clicks were done at a higher rate for left-identifying respondents, but non-left respondents more frequently indicated that they would view and write replies. This continues a trend of individuals crossing ideological lines to engage with tweets (albeit in just a few, specific ways) more frequently than individuals whose ideological stances align more closely with the message of the tweet.

```{r}
gen_engagement_graph(13)

```

Tweet 13 attempted to bring attention to the fact that Donald Trump, whom the author called a white supremacist, has been responsible for placing three judges on the Supreme Court. The tweet was ignored by over 80% of non-left respondents, which may explain why left-identifying respondents performed every type of engagement much more frequently than non-left respondents.

```{r}
gen_engagement_graph(14)

```

Tweet 14 was written by a radio show host advertising his podcast in which he and his co-host "talk the coronavirus hoax, and how masks are merely symbolic, and do nothing to protect you". Despite the significant emotional energy contained in this tweet, over 70% of respondents from both groups ignored the tweet, with the only significant form of engagement being viewing replies, which over 20% of respondents from both categories indicated they would do.

```{r}
gen_engagement_graph(15)

```

Tweet 15 is a proclamation by Rep. Matt Gaetz that Donald Trump is leading the fight against corruption and against "the establishment". The tweet was ignored often by both left-identifying and non-left respondents (over 80% and 60% respectively), but when it was engaged with, it was engaged with much more frequently than non-left respondents in just about every way. The only significant engagement that left-identifying respondents seem to perform was viewing the tweets replies, which they opted to do just under 12.5% of the time.

```{r}
gen_engagement_graph(16)

```

Tweet 16 points out the fallacy in claiming that wearing a mask in the midst of a pandemic is tyranny, but that an 8pm curfew in the midst of a protest isn't -- clearly a left-leaning message. This tweet was liked and retweeted relatively frequently by left-identifying respondents (almost 60%  and 20% of the time, respectively), but while the portion of non-left respondents that liked the tweet was around 10%, the portion that desired to retweet was nearly 15%: an interesting discrepancy given that retweeting generally shows more support for a message than does liking a tweet, and given that the tweet's message aligns much more with the left than the right. Another interesting feature of this graph is the proportion of non-left respondents that indicated they wished to view the replies of the tweet, 30%, especially compared to the smaller proportion of left-identifying respondents who indicated wanting to do the same. 

```{r}
gen_engagement_graph(17)

```

Tweet 17 accuses conservatives of "loving" violence given their defense of their decision to own firearms all while they patronize the left for engaging in non-peaceful protests. Almost 80% of the non-left respondents indicated that they would ignore the tweet, but still a significant number of these resepondents, nearly 20%, indicated that they wished to view the tweet's replies. Non-left respondents were also significantly more likely to write replies than left-identifying respondents, who had higher frequencies of every other kind of engagement.

```{r}
gen_engagement_graph(18)
```
The last tweet of the corpus criticizes the left's claim that Mitch McConnell's attempt to rapidly push in Donald Trump's latest Supreme Court justice is hypocritical, saying that the claim is baseless because doing so is the senate's job. Non-left respondents engaged with the tweet more frequently in every form of engagement apart from one: viewing replies. Both left-identifying and non-left respondents indicated they wanted to view the tweet's replies over 20% of the time, with left-identifying respondents doing so slightly more frequently. 



The 18 tweets above have proven to give mixed results. Political belief seemed to be a decent predictor of users' choices to like, retweet, or ignore the tweet, where users seemed to do the former two when the tweet's message aligned with their beliefs, and did the latter when it did not. We can verify these patterns by summarizing all 18 of the above tweets into one larger graph, which shows how users of each group, left and not left, engaged with tweets of each kind, left and right:

```{r}
data %>%
  mutate(tweet_type = case_when(
    Tweet %in% c(1, 2, 5, 7, 9, 12, 13, 16, 17) ~ "Left",
    TRUE ~ "Right"
  )) %>%
  mutate(response_type = case_when(
    tweet_type == "Left" & political_group == "Left" ~ "Left Respondent to Left Tweet",
    tweet_type == "Left" & political_group == "Not Left" ~ "Non-left Respondent to Left Tweet",
    tweet_type == "Right" & political_group == "Left" ~ "Left Respondent to Right Tweet",
    tweet_type == "Right" & political_group == "Not Left" ~ "Non-left Respondent to Right Tweet"
  )) %>%
    select(Engagement_Like, Engagement_Retweet.with.quote, Engagement_Retweet.without.quote, Engagement_Click.on.author.s.profile, Engagement_View.replies, Engagement_Write.reply, Engagement_Ignore.keep.scrolling, response_type) %>%
    group_by(response_type) %>%
    summarise(
      like_proportion = mean(Engagement_Like),
      rt_without_proportion = mean(Engagement_Retweet.without.quote),
      rt_with_proportion = mean(Engagement_Retweet.with.quote),
      click_profile_proportion = mean(Engagement_Click.on.author.s.profile),
      view_replies_proportion = mean(Engagement_View.replies),
      write_replies_proportion = mean(Engagement_Write.reply),
      ignore_proportion = mean(Engagement_Ignore.keep.scrolling)
    ) %>%
    gather(key = Engagement, value = Proportion, like_proportion:ignore_proportion) %>%
    ggplot(aes(Engagement, Proportion, fill = response_type)) + geom_col(position = "dodge")+ coord_flip() 

 

```

As was observed manually through the 18 tweets above, left-identifying respondents were much more likely to like and retweet left-aligned tweets than they were for right-aligned tweets. They also ignored right-aligned tweets far more often than they ignored left-aligned tweets, but they viewed the replies of left-aligned tweets almost exactly as often as they viewed the replies of right-aligned tweets. 

Meanwhile, non-left respondents liked right-aligned tweets almost exactly as frequently as they liked left-aligned tweets. This may be due to the fact that centrists make up a significant portion of the non-left population, but even then, the fact that the conservative portion of the non-left respondents didn't create any sort of separation between the two categories of tweets is intriguing to say the last. There also wasn't much separation between the frequencies at which non-left respondents ignored left-aligned and right-aligned tweets, and the same seems to hold true for retweets and ignoring tweets. As was the case with the left-identifying respondents, though, non-left respondents marked "view replies" at about the same frequency for both categories of tweets. 

THEN ANSWER BIG POINT
The following 


THEN LAST BIT



THINGS THAT I WANT TO TEST:
- Compare political ideology to engagement for each tweet
- Emotional response vs engagement, compare between political parties


## Analysis of Results
- Engagement with controversial tweets - cite example of tweet 6 - viewing replies = more engagement, which likely results in more time spent on the app = algorithm more likely to recommend similar tweets to those users - same with 14 (hoax radio hosts)
- Tweet 8 - Gaetz - leftists being more likely to view replies (as with tweet 11 about Kavanaugh), write reply, click on profile
- Trends - non-left respondents seemed more likely to homogenously/monolithically/uniformly ignore tweets in large numbers
- HUGE TREND - political messaging of the tweet didn't really seem to sway the engagement of non-left respondents. Centrists? Perhaps right-aligned tweets were to extreme for the mostly moderately conservative students?

## Conclusion



